Linear regression for approximating real and synthetic data

### 2022-10-11 doc/paper.tex
More paper

\usepackage{graphicx} %% for loading jpg figures
\usepackage{bm}
\usepackage{nicefrac}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{parskip}
\usepackage{listings}
\usepackage{float}
\usepackage{xcolor}

@@

%%% first author
\author{Jonatan H. Hanssen
    \affiliation{
	Bachelor Student, Robotics and Intelligent Systems\\
	The faculty of Mathmatics and Natural Sciences\\
	Department of Informatics\\
    Email: jonatahh@ifi.uio.no
    }
}

\author{Eric E. Reber
    \affiliation{
	Bachelor Student, Robotics and Intelligent Systems\\
	The faculty of Mathmatics and Natural Sciences\\
	Department of Informatics\\
    Email: ericer@ifi.uio.no
    }
}

@@

Using Ridge regression, we see from Fig.~\ref{frankiedifflambdas} that larger and larger values of $\lambda$ efficiently prevents overfitting and reduces the variance between predictions. Looking at the beta progression with for the same values of $\lambda$ (Fig.~\ref{frankeridgebetas}), we see that the regularization parameter is successfully shrinking the beta values. Using Scikit's gridsearch, we find the optimal $\lambda$ to be $10^{-8}$ and the optimal polynomial degree to be 7, with an average MSE of $0.0037999$, which is very slightly lower than OLS for the Franke function with an added stochastic noise $\epsilon \sim N(0,0.05)$. We see from this that Ridge regression has not really had much of an effect in decreasing the MSE. We must now remember what Ridge aims to do. With the regularization parameter, we can prevent overfitting if our model is too complex for our data. Looking at Fig.~\ref{frankeridgenoisecomparison} in comparison to Fig.~\ref{frankienoisecomparison} (both in the appendix), we can see that Ridge really has achieved this, reducing overfitting as our data becomes more and more noisy. But we should recall that we decide the complexity of our model, by deciding which polynomial degree we use when creating the design matrix. In fact, by choosing polynomial degree 7 for our OLS method to get the best MSE for noisy data, we are in fact doing a primitive form of best subset selection, as described in Hastie et Al.\cite[57]{hastie}. Almost by definition, the polynomial degree with the best MSE is not overfitted, because if it was, it would not be the model with the lowest MSE among all polynomial degrees. Therefore it is not so unexpected that Ridge regression has a relatively low impact on the MSE. We could expect that Ridge would allow us to reach higher polynomial degrees without overfitting, by shrinking features of the higher polynomial degrees that are not supported but allowing us to keep other high degree terms (for example, allowing us to use $x^5y^4$, but discard $x^9$, if only $x^5y^4$ was supported by the data). But we can see from the Table. ~\ref{ols_vs_ridge_vs_lasso_table} that we are not able to push into higher degrees. A possible explanation for this is that every feature is useful, due to the polynomial expansion of the Franke function.

% \begin{table}[t]
% \caption{Best MSE for Ridge regression and OLS with 400 datapoints}
% \begin{center}
% \label{ols_vs_ridge_table}
% \begin{tabular}{c | l l l l}
% % & & \\ % put some space after the caption
% % \hline
% Regression & Std of noise & MSE & Degree & $\lambda$ \\
% \hline
% OLS & 0.05 & 0.0038302 & 7 & - \\
% Ridge & 0.05 & 0.0037999 & 7 & $10^{-8}$ \\
% \hline
% \end{tabular}
% \end{center}
% \end{table}

@@

\begin{figure} 
\centerline{\includegraphics[width=3.25in]{figure/frankiedifflambdas.png}}
\caption{Bias, variance and test MSE plotted over polynomial degree for our Ridge prediction on the Franke function with an added stochastic noise $\epsilon \sim N(0,0.05)$, using lambdas of increasing size. Here we have reduced the number of datapoints to only 100 to force overfitting earlier.}
\label{frankiedifflambdas}
\end{figure}

\begin{figure} 
\centerline{\includegraphics[width=3.25in]{figure/frankeridgebetas.png}}
\caption{Beta progression for different values of lambda in Ridge regression. Note the different scales on each of the plots, showing how increasing the regularization parameter shrinks the betas}
\label{frankeridgebetas}
\end{figure}

@@

Here we find some limitations of linear regression. We see from Fig.~\ref{real1msetraintest} that the we are able to fit the terrain up to a certain point, gaining an MSE of $0.0142683$ with OLS with polynomial degree 19. This is about two orders of magnitude higher than our lowest MSE for the Franke function without noise, which had values on a similar scale.\footnote{The Franke function without noise has a range of about $(0,1.2)$ and our MinMaxed terrain data has been scaled to a range of $(0,1)$. While not exactly the same, these are on the same order of magnitude, and we believe that comparing the MSE scores is reasonable} In fact, our MSE is comparable to the Franke function with a stochastic noise $\epsilon \sim N(0,0.1)$, which implies that our terrain is very irregular and difficult to approximate. Looking at the plot for polynomial degree 19 (Fig.~\ref{real1surfacecomp}), we see that our poor MSE is reflected visually in our fit as well, as the surfaces do not look particularly similar. Comparing the best polynomial degree of the best fit with the synthetic data, we see that our best fit is reached much later. This implies that we are not overfitting yet, and indeed the bias variance decomposition confirms this, as we see that variance is essentially inconsequential (Fig.~\ref{realbiasvarianceOLS}). %This can be seen when we increase the polynomial degree to very large amounts, without seeing any decrease in MSE (Fig. NUMBER). Looking at the beta progression for selected betas (Fig. NUMBER), we see that the parameters stabilize, which implies that we are not overfitting, but simply reaching our best possible prediction for polynomial regression. The fact that we are not overfitting is further reinforced by looking at the bias-variance plot in Fig.~\ref{realbiasvarianceOLS}, which shows no increase in variance. 
It is reasonable to expect that our model will not overfit, due to the large increase in data we now use for the fit. Our synthetic data used $20 x 20 = 400$ datapoints, while we now have $320 x 640 = 204 800$ datapoints. This means that for a 50th order polynomial, which will have $1326$ features, our number of features are less than $1\%$ of our datapoints. If we decrease the number of datapoints used for training considerably, we can see overfitting start to occur (Fig.~\ref{real1mselessdata} in the appendix). So we are not overfitting, but we are not decreasing our MSE either. This is likely because the elevation data has a jagged and complex shape, which cannot be accurately recreated, even with a polynomial of degree $50$. We should remember that the Franke function can be expanded into a series of polynomials, which is why we can expect to get a lower and lower MSE as the polynomial degree increases (so long as we have enough data and it is not noisy). The same is not true for our elevation data, and as such we have little to gain from increasing our model complexity after a certain point. Clearly, linear regression does not offer a very good tradeoff between computational cost and performance for this data.

@@

\begin{figure} 
\centerline{\includegraphics[width=3.25in]{figure/real1msetraintest.png}}
\caption{Test and train MSE for OLS on Terrain 1}
\label{real1msetraintest}
\end{figure}

% \begin{figure} 
% \centerline{\includegraphics[width=3.25in]{figure/realmse.png}}
% \caption{Test and train MSE }
% \label{frankiedifflambdas}
% \end{figure}

@@

As our model is not overfitting, we do not expect Ridge to offer much improvement.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% begin figure %%%%%%%%%%%%%%%%%%%
% \begin{figure}[t]
% \begin{center}
% \setlength{\unitlength}{0.012500in}%
% \begin{picture}(115,35)(255,545)
% \thicklines
% \put(255,545){\framebox(115,35){}}
% \put(275,560){Beautiful Figure}
% \end{picture}
% \end{center}
% \caption{The caption of a single sentence does not have period at the end}
% \label{figure_ASME} 
% \end{figure}
%%%%%%%%%%%%%%%% end figure %%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%% begin figure %%%%%%%%%%%%%%%%%%%
% \begin{figure} 
% \centerline{\includegraphics[width=3.34in]{figure/FMANU_MD_05_1272_5.jpg}}
% \caption{While this figures is easily readable at a double column width of 6.5in, when it is shrunk to 3.25in column width the text is unreadable. This paper was held from production.}
% \label{fig_example2.jpg}
% \end{figure}
%%%%%%%%%%%%%%%% end figure %%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%% begin figure %%%%%%%%%%%%%%%%%%%
%%% the maximum width in double column is 6.85in
% \begin{figure*} 
% \centerline{\includegraphics[width=6.85in]{figure/FMANU_MD_04_1274_13.jpg}}
% \caption{A figure expanded to double column width the text from Figure~\ref{fig_example3.jpg}}
% \label{fig_example4.jpg}
% \end{figure*}
%%%%%%%%%%%%%%%% end figure %%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table*}
\caption{This table shows every applicable parameter for every figure, so that they may be easily reproduced. Every plot uses the random seed 42069}
\begin{center}
\label{allparamstable}
\begin{tabular}{c | l l l l l l l}
% & & \\ % put some space after the caption
% \hline
Figure & Highest $N$ & Std of noise & Step (\# of points) & Bootstraps & K-folds & $\lambda$ & Scaling \\
\hline
\ref{frankiedifflambdas} & 25 & 0.05 & 0.1 (100) & 100 & - & variable & Centering\\
\ref{frankeridgebetas} & 25 & 0.05 & 0.1 (100) & - & - & variable & Centering\\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}
\caption{This table shows the command to execute, as well as the advanced parameters to change, to reproduce every figure in the report. (More info about the scripts and their parameters can be found in the README)}
\begin{center}
\label{allparamstable}
\begin{tabular}{c | l l l l}
% & & \\ % put some space after the caption
% \hline
Figure & Shell command (leading \texttt{python3} omitted) & Bootstraps & K-folds & $\lambda$ \\
\hline
\ref{frankenonoise} & \texttt{task\_b.py --noise 0 -n 25} & - & - & - \\
\ref{frankenonoisemse} & \texttt{task\_c.py --noise 0 -n 25}  & 100 & - & - \\
\ref{frankenoisemse} & \texttt{task\_c.py -n 25}  & 100 & - & - \\
\ref{frankiebiasvariance} & \texttt{task\_c.py -n 25 --step 0.1}  & 100 & - & - \\
\ref{frankenoisybeta} & \texttt{task\_c.py -n 25}  & 100 & - & - \\
\ref{frankienoisecomparison} & \texttt{noise\_plot.py} & 100 & - & - \\
\ref{frankiehigherdatapoints} & \texttt{task\_c.py --noise 0 -n 30 --step 0.01} & 100 & - & - \\
\ref{real1surfacecomp} & \texttt{task\_b.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 19} & - & - & - \\
\ref{real1mselessdata} & \texttt{task\_c.py -f ../data/tiny\_SRTM\_data\_Norway\_1.tif -n 20} & 100 & - & - \\
\hline
\end{tabular}
\end{center}
\end{table*}

@@

\begin{figure*}
% \begin{figure}[t]
\centerline{\includegraphics[width=3.25in]{figure/real1mselessdata.png}}
\caption{Test and train MSE for the OLS prediction of terrain 1, this time downscaled to only $50x100$. Here the optimal degree was 11, showing that with lower data we start to overfit more rapidly.}
\label{real1mselessdata}
\end{figure*}

\begin{figure*}
% \begin{figure}[t]
\centerline{\includegraphics[width=3.25in]{figure/frankeridgenoisecomparison.png}}
\caption{Test and train MSE for the Ridge prediction with $\lambda = 10^{-8}$ of the Franke function with an increasing amount of noise}
\label{frankeridgenoisecomparison}
\end{figure*}

\begin{figure*}
% \begin{figure}[t]
\centerline{\includegraphics[width=3.25in]{figure/frankiehigherdatapoints.png}}
\caption{Franke function fitted up to polynomial degree 30, with 10000 datapoints instead of 400. As we can see, we do not overfit even at this polynomial degree when the availiable data is plentiful. The highest MSE was reached at $N=29$, and was $0.00003511$, one tenth of our best prediction with only 400 datapoints}
\label{frankiehigherdatapoints}
\end{figure*}

\begin{figure*}
% \begin{figure}[t]
\centerline{\includegraphics[width=3.25in]{figure/frankenoisybeta.png}}
\caption{Beta progression for OLS}
\label{frankenoisybeta}
\end{figure*}

>>>>

\usepackage{graphicx} %% for loading jpg figures
\usepackage{bm}
\usepackage{nicefrac}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{parskip}
\usepackage{listings}
\usepackage{tablefootnote}
\usepackage{float}
\usepackage{xcolor}

@@

%%% first author
\author{Jonatan H. Hanssen
    \affiliation{
	Bachelor Student, Robotics and Intelligent Systems\\
	Department of Informatics\\
	The faculty of Mathmatics and Natural Sciences\\
    Email: jonatahh@ifi.uio.no
    }
}

\author{Eric E. Reber
    \affiliation{
	Bachelor Student, Robotics and Intelligent Systems\\
	Department of Informatics\\
	The faculty of Mathmatics and Natural Sciences\\
    Email: ericer@ifi.uio.no
    }
}

@@

Using Ridge regression, we see from Fig.~\ref{frankiedifflambdas} in the appendix that larger and larger values of $\lambda$ efficiently prevents overfitting and reduces the variance between predictions. Looking at the beta progression with for the same values of $\lambda$ (Fig.~\ref{frankeridgebetas} in the appendix), we see that the regularization parameter is successfully shrinking the beta values. Using Scikit's gridsearch, we find the optimal $\lambda$ to be $10^{-8}$ and the optimal polynomial degree to be 7, with an average MSE of $0.0037999$, which is very slightly lower than OLS for the Franke function with an added stochastic noise $\epsilon \sim N(0,0.05)$. We see from this that Ridge regression has not really had much of an effect in decreasing the MSE. We must now remember what Ridge aims to do. With the regularization parameter, we can prevent overfitting if our model is too complex for our data. Looking at Fig.~\ref{frankeridgenoisecomparison} in comparison to Fig.~\ref{frankienoisecomparison} (both in the appendix), we can see that Ridge really has achieved this, reducing overfitting as our data becomes more and more noisy. But we should recall that we decide the complexity of our model, by deciding which polynomial degree we use when creating the design matrix. In fact, by choosing polynomial degree 7 for our OLS method to get the best MSE for noisy data, we are in fact doing a primitive form of best subset selection, as described in Hastie et Al.\cite[57]{hastie}. Almost by definition, the polynomial degree with the best MSE is not overfitted, because if it was, it would not be the model with the lowest MSE among all polynomial degrees. Therefore it is not so unexpected that Ridge regression has a relatively low impact on the MSE. We could expect that Ridge would allow us to reach higher polynomial degrees without overfitting, by shrinking features of the higher polynomial degrees that are not supported but allowing us to keep other high degree terms (for example, allowing us to use $x^5y^4$, but discard $x^9$, if only $x^5y^4$ was supported by the data). But we can see from the Table. ~\ref{ols_vs_ridge_vs_lasso_table} that we are not able to push into higher degrees. A possible explanation for this is that every feature is useful, due to the polynomial expansion of the Franke function.

@@

@@

Here we find some limitations of linear regression. We see from Fig.~\ref{real1msetraintest} that the we are able to fit the terrain up to a certain point, gaining an MSE of $0.0142683$ with OLS with polynomial degree 19. This is about two orders of magnitude higher than our lowest MSE for the Franke function without noise, which had values on a similar scale.\footnote{The Franke function without noise has a range of about $(0,1.2)$ and our MinMaxed terrain data has been scaled to a range of $(0,1)$. While not exactly the same, these are on the same order of magnitude, and we believe that comparing the MSE scores is reasonable} In fact, our MSE is comparable to the Franke function with a stochastic noise $\epsilon \sim N(0,0.1)$ (Table.~\ref{ols_mse_table_dif_data}), which implies that our terrain is very irregular and difficult to approximate. Looking at the plot for polynomial degree 19 (Fig.~\ref{real1surfacecomp}), we see that our poor MSE is reflected visually in our fit as well, as the surfaces do not look particularly similar. Comparing the best polynomial degree of the best fit with the synthetic data, we see that our best fit is reached much later. This implies that we are not overfitting yet, and indeed the bias variance decomposition confirms this, as we see that variance is essentially inconsequential (Fig.~\ref{realbiasvarianceOLS}). %This can be seen when we increase the polynomial degree to very large amounts, without seeing any decrease in MSE (Fig. NUMBER). Looking at the beta progression for selected betas (Fig. NUMBER), we see that the parameters stabilize, which implies that we are not overfitting, but simply reaching our best possible prediction for polynomial regression. The fact that we are not overfitting is further reinforced by looking at the bias-variance plot in Fig.~\ref{realbiasvarianceOLS}, which shows no increase in variance. 
It is reasonable to expect that our model will not overfit, due to the large increase in data we now use for the fit. Our synthetic data used $20 x 20 = 400$ datapoints, while we now have $320 x 640 = 204 800$ datapoints. This means that for a 20th order polynomial, which will have $231$ features, we will have around a thousand datapoints per feature. If we decrease the number of datapoints availiable considerably, we can see overfitting start to occur (Fig.~\ref{real1mselessdata} in the appendix). So we are not overfitting, but we are not decreasing our MSE either. This is likely because the elevation data has a jagged and complex shape, which cannot be accurately recreated, even with a polynomial of degree $50$. We should remember that the Franke function can be expanded into a series of polynomials, which is why we can expect to get a lower and lower MSE as the polynomial degree increases (so long as we have enough data and it is not noisy). The same is not true for our elevation data, and as such we have little to gain from increasing our model complexity after a certain point. Clearly, linear regression does not offer a very good tradeoff between computational cost and performance for this data.

\begin{table}[t]
\caption{Best MSE and polynomial degree for OLS on synthetic and real data}
\begin{center}
\label{ols_mse_table_dif_data}
\begin{tabular}{c l l l}
Dataset & Std of noise & Best MSE & Best degree \\
\hline
Franke & 0 & 0.0005109 & 9\\
Franke & 0.05 & 0.0038302 & 7 \\
Franke & 0.10 & 0.0139833 & 7 \\
Terrain 1 & - & 0.0142683 & 19 \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure} 
\centerline{\includegraphics[width=3.25in]{figure/real1msetraintest.png}}
\caption{Test and train MSE for OLS on Terrain 1}
\label{real1msetraintest}
\end{figure}
\begin{figure} 
\centerline{\includegraphics[width=3.25in]{figure/real1msetraintest.png}}
\caption{Test and train MSE for OLS on Terrain 1}
\label{real1msetraintest}
\end{figure}

@@

As our model is not overfitting, we do not expect Ridge to offer much improvement. This proves to be the case, as we see from Fig.~\ref{real1ridgedifflambdas}. Here we see that for low values of lambda there is no improvement, as there are no parameters that need regularization, and no overfitting to supress. For larger values, we see that we are shrinking the parameters too much, and we see an increase in MSE. We could expect to see that Ridge shows improvement at higher polynomial degrees, when OLS starts to overfit, but due to computational constraints we have not been able to push much further than 20 degrees.

With lasso regression, we see similar results as with Ridge. Comparing all the three method, we see again that OLS comes out on top. This time, it is not because we pick the polynomial degree that does not overfit, but because we are not overfitting at the highest degree we are using for our prediction. See Table.~\ref{ols_vs_ridge_vs_lasso_table_real}.

\begin{figure} 
\centerline{\includegraphics[width=3.25in]{figure/real1ridgedifflambdas.png}}
\caption{Test and train MSE for OLS on Terrain 1}
\label{real1ridgedifflambdas}
\end{figure}

\begin{table*}[t]
\caption{Best MSE for OLS, Ridge and Lasso regression on real elevation data}
\begin{center}
\label{ols_vs_ridge_vs_lasso_table_real}
\begin{tabular}{c | l l l}
Regression & MSE & Degree & $\lambda$ \\
\hline
OLS & 0.0142683 & 19 & - \\
Ridge & 0.017034 & 7 & $10^{-8}$ \\
Lasso & 0.0095846 & 10 & $2.5118 \cdot 10^{-6}$ \\
\hline
\end{tabular}
\end{center}
\end{table*}

\section{Conclusion}

In this paper we have compared Ordinary Least Squares, Ridge and Lasso regression for both synthetic and real data. We have found that linear regression was well suited for approximating the synthetic Franke function, but less suited for the real elevation data. We have seen that Ridge and Lasso gives us the ability to prevent overfitting for more complex models, but that they have little to offer in this case, due to our ability to easily reduce or increase the complexity of our model, and due to the nature of our data. We have also seen the value of using regression methods such as bootstrap and cross validation to learn valuable insights about the quality of our predictions.

@@

\begin{table*}
\caption{This table shows the command to execute, as well as the advanced parameters to change, to reproduce every figure in the report. (More info about the scripts and their parameters can be found in the README)}
\begin{center}
\label{allparamstable}
\begin{tabular}{c | l l l l}
Figure & Shell command (leading \texttt{python3} omitted) & Bootstraps & K-folds & $\lambda$ \\
\hline
\ref{frankenonoise} & \texttt{task\_b.py --noise 0 -n 25} & - & - & - \\
\ref{frankenonoisemse} & \texttt{task\_c.py --noise 0 -n 25}  & 100 & - & - \\
\ref{frankenoisemse} & \texttt{task\_c.py -n 25}  & 100 & - & - \\
\ref{frankiebiasvariance} & \texttt{task\_c.py -n 25 --step 0.1}  & 100 & - & - \\
\ref{frankiedifflambdas} & \texttt{task\_e\_biasvariance.py -n 25}  & 100 & - & - \\
\ref{frankeridgebetas} & \texttt{task\_e\_betas.py -n 25}  & 100 & - & - \\
\ref{frankenoisybeta} & \texttt{task\_c.py -n 25}  & 100 & - & - \\
\ref{frankienoisecomparison} & \texttt{noise\_plot.py} & 100 & - & - \\
\ref{frankeridgenoisecomparison} & \texttt{noise\_plot.py} \footnotesize{(\it Model has been changed to ridge with lambda=$10^{-8}$)} & 100 & - & - \\
\ref{frankiehigherdatapoints} & \texttt{task\_c.py --noise 0 -n 30 --step 0.01} & 100 & - & - \\
\ref{real1surfacecomp} & \texttt{task\_b.py --file ../data/small\_SRTM\_data\_Norway\_1.tif -n 19} & - & - & - \\
\ref{real1mselessdata} & \texttt{task\_c.py -f ../data/tiny\_SRTM\_data\_Norway\_1.tif -n 20} & 100 & - & - \\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{figure*} 
\centerline{\includegraphics[width=3.25in]{figure/frankeridgebetas.png}}
\caption{Beta progression for different values of lambda in Ridge regression. Note the different scales on each of the plots, showing how increasing the regularization parameter shrinks the betas}
\label{frankeridgebetas}
\end{figure*}

\begin{figure*} 
\centerline{\includegraphics[width=3.25in]{figure/frankiedifflambdas.png}}
\caption{Bias, variance and test MSE plotted over polynomial degree for our Ridge prediction on the Franke function with an added stochastic noise $\epsilon \sim N(0,0.05)$, using lambdas of increasing size. Here we have reduced the number of datapoints to only 100 to force overfitting earlier.}
\label{frankiedifflambdas}
\end{figure*}

@@

\begin{figure*}
\centerline{\includegraphics[width=3.25in]{figure/frankeridgenoisecomparison.png}}
\caption{Test and train MSE for the Ridge prediction with $\lambda = 10^{-8}$ of the Franke function with an increasing amount of noise}
\label{frankeridgenoisecomparison}
\end{figure*}

\begin{figure*}
\centerline{\includegraphics[width=3.25in]{figure/real1mselessdata.png}}
\caption{Test and train MSE for the OLS prediction of terrain 1, this time downscaled to only $50x100$. Here the optimal degree was 11, showing that with lower data we start to overfit more rapidly.}
\label{real1mselessdata}
\end{figure*}

\begin{figure*}
\centerline{\includegraphics[width=3.25in]{figure/frankiehigherdatapoints.png}}
\caption{Franke function fitted up to polynomial degree 30, with 10000 datapoints instead of 400. As we can see, we do not overfit even at this polynomial degree when the availiable data is plentiful. The highest MSE was reached at $N=29$, and was $0.00003511$, one tenth of our best prediction with only 400 datapoints}
\label{frankiehigherdatapoints}
\end{figure*}

\begin{figure*}
\centerline{\includegraphics[width=3.25in]{figure/frankenoisybeta.png}}
\caption{Beta progression for OLS}
\label{frankenoisybeta}
\end{figure*}
